Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-16 paper/ms.tex
editting ACF section

%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
%\end{center} 
%\caption{Best models when both the constraints on the maximal number
%  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
%  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
%\end{figure*}

@@

The measurementens presented in \citep{Yamada2012} do not present a
new measurement of the angular correlation function (ACF). However
\citep{Hayashino2004} performed such calculation on the LAEs observed
in the densest field of SSA22.

we calculate the angular correlation function
(ACF) for all the models having the $15$ mock surveys consistent with
observations. We perform this calculation as a sanity check and
potential additional constraint. The ACF is computed only the densest
subfield in all the 15 mock surveys corresponding to the SSA22
region.

@@

The comparison between the simulated and observed ACFs is also done using a
$\chi^2$ statistic which includes the information on the measurement
uncertainties and the statistical dispersio from the $15$ mock surveys
in the simulation

\begin{equation}
\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
    sim}^2({\theta_i})}, 
\end{equation}

where the sum is done over all the $13$ angle values $\theta_i$ where the
ACF has been computed. In Figure XX we plot this statistic for all the
models considered. In all cases $\chi^{2}<7$ which is not sufficient
to consider that the correlation functions from the simulations are
statistically different from the observational one. The constribution
of cosmic variance in the simulations together with the statistical
uncertainties make all tested models compatible with the observational
constraints.

We also present the results for the mean angular correlation function in
therms of the angular correlation lenght obtained  by fitting to a power-law
function:

@@

The fitting is done to both the mean ACF and the observational
ACF reported by \cite{Hayashino2004} .  The results are shown 
in Figure  \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$ 
plane where the average and standard deviation for each mock 
are shown in comparison with the result derived from observations. 
Error bars in these figures represents the standard deviation of the
ACF over all the sub-fields.

It can be seen in the left panel figure \ref{figure:correlation_parameters} that
The observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
constrains on the parameters models. Only models with angular-correlation lenght within  
$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models.

@@

>>>>

@@

We impose an additional constraint by requiring that the models
selected in the previous section to be also compatible with the
observational ACF. The measurementens presented in \citep{Yamada2012}
do not present a new measurement of the angular correlation function
(ACF). Instead we use the measurements performed by
\citep{Hayashino2004} on the LAEs observed in the densest field of
SSA22.

@@

The comparison between the theoretical and observational ACF is done in
therms of the angular correlation lenght obtained  by fitting to a power-law
function:

@@

The procedure is a done through a least square minimizatio is done to
both the mean ACF and the observational ACF reported by
\cite{Hayashino2004} .  The results are shown  in Figure
\ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$  plane
where the average and standard deviation for each mock  are shown in
comparison with the resut derived from observations.  Error bars in
these figures represents the standard deviation of the ACF over all
the sub-fields. These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

We see in the left panel Figure \ref{figure:correlation_parameters} that
the observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
constrains on the parameters models. Only models with angular-correlation lenght within  
$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models.

@@

%The comparison between the simulated and observed ACFs is also done using
%$\chi^2$ statistic which includes the information on the measurement
%uncertainties and the statistical dispersio from the $15$ mock surveys
%in the simulation

%\begin{equation}
%\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
%    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
%    sim}^2({\theta_i})}, 
%\end{equation}

%where the sum is done over all the $13$ angle values $\theta_i$ where the
%ACF has been computed. In Figure XX we plot this statistic for all the
%models considered. In all cases $\chi^{2}<7$ which is not sufficient
%to consider that the correlation functions from the simulations are
%statistically different from the observational one. The constribution
%of cosmic variance in the simulations together with the statistical
%uncertainties make all tested models compatible with the observational
%constraints.
